### 2014-06-12 paper/body.tex
changes from Yoshua

\begin{enumerate}
\item We propose one way of answering the first question above through the degree to which features from one dataset transfer to another (Section~\ref{sec:definition}). We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we systematically characterize the general to specific transition, which yields the next three results.
\item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves. In different regions of the network, we show how different effects dominate (Section~\ref{sec:experiments_ab}).
\item We show how the transferability gap grows as the distance between base
task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009} (Section~\ref{sec:experiments_random_nm}).
\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
\end{enumerate}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.65\linewidth]{plots/result_random_nm_combined_crop.pdf}
\end{center}
\caption{Performance degredation vs. layer; see text for details. (top left): random fixed features. (top right): a manual split of ImageNet into natural vs. man-made groups. (bottom): the top two plots normalized by their base performance and compared to the \dA/\dB split from Section~\ref{sec:experiments_ab} (in red).}
\label{fig:random_and_nm}
\end{figure}

>>>>

\begin{enumerate}
\item We propose one way of answering the first question above through the degree to which features from one dataset transfer to another (Section~\ref{sec:definition}). We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
Others have loosely addressed the question of generality by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we systematically characterize the general to specific transition, which yields the next three results.
\item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves. In different regions of the network, we show how different effects dominate (Section~\ref{sec:experiments_ab}).
\item We show how the transferability gap grows as the distance between base
task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009} (Section~\ref{sec:experiments_random_nm}).
\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
\end{enumerate}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.65\linewidth]{plots/result_random_nm_combined_crop.pdf}
\end{center}
\caption{Performance degradation vs. layer; see text for details. (top left): random fixed features. (top right): a manual split of ImageNet into natural vs. man-made groups. (bottom): the top two plots normalized by their base performance and compared to the \dA/\dB split from Section~\ref{sec:experiments_ab} (in red).}
\label{fig:random_and_nm}
\end{figure}
